% !TEX program = xelatex

\documentclass{resume}
%\usepackage{zh_CN-Adobefonts_external} % Simplified Chinese Support using external fonts (./fonts/zh_CN-Adobe/)
%\usepackage{zh_CN-Adobefonts_internal} % Simplified Chinese Support using system fonts

\begin{document}
\pagenumbering{gobble} % suppress displaying page number

\name{Liang Tang}

\basicInfo{
  \email{shinytang6@gmail.com} \textperiodcentered\
  \phone{(+86) 18221865643} \textperiodcentered\
  }

\section{\faGraduationCap\ Education}
\datedsubsection{\textbf{Shanghai Jiao Tong University (SJTU)}, Shanghai, China}{Sep. 2015 -- Present}
\textit{B.S.} in Information Security (IS), expected June 2019

\section{\faBuilding\ Working Experience}

\datedsubsection{\textbf{neoBay} Shanghai, China}{June. 2017 -- Aug. 2017}
\role{Summer Internship}{Software Engineering Intern}
\begin{itemize}
  \item Implemented a high-precision rights control system to ensure your files in the right place.
  \item Maintain the Website of neoBay.
\end{itemize}

\section{\faUsers\ Selected Projects}

\datedsubsection{\textbf{p5.js web editor}}{Feb. 2018 -- Present}
\role{Mongodb, Express, React/Redux, Nodejs}{Open source contributor}
\begin{itemize}
  \item Enhance functionality of the web editor for p5.js.
\end{itemize}
Available at https://github.com/processing/p5.js-web-editor/commits/master?author=shinytang6


\datedsubsection{\textbf{Sniffer}}{Dec. 2017 -- Jan. 2018}
\role{C++}{Individual Project}
\begin{itemize}
  \item Implemente a network packet sniffer with GUI (Qt5 and Wincap).
  \item Support packet filter/query, import/export packets and reassemble TCP packets.
\end{itemize}
Available at https://github.com/shinytang6/Sniffer


\datedsubsection{\textbf{Logico}}{Nov. 2017}
\role{Golang}{Individual Project}
A project aims at optimizimg users' reading experience, created at Go Hack 2017.
\begin{itemize}
  \item Render different colors based on part of speech in an article.
\end{itemize}
Available at https://github.com/shinytang6/Logico


\datedsubsection{\textbf{Campus-Information-Platform}}{Nov. 2017 -- Dec. 2017}
\role{Laravel, Vue}{Course Project}
A project aims at helping college students collect information on activities.\begin{itemize}
  \item Posting activities and events held inside or outside campus.
  \item Support subscription function and push regular events on a regular basis.
\end{itemize}
Available at https://github.com/SE407-2017/campus-information-platform



\datedsubsection{\textbf{imoocMovie}}{May. 2017}
\role{Nodejs}{Individual Project}
Imooc Movie Website\\
Available at https://github.com/shinytang6/imoocMovie


\datedsubsection{\textbf{studentManageSystem}}{April. 2017 -- May. 2017}
\role{PHP}{Course Project}
A project aims at managing student status.\\
Available at https://github.com/shinytang6/studentManageSystem
\\
\\
More work can be seen here: https://github.com/shinytang6

% Reference Test
%\datedsubsection{\textbf{Paper Title\cite{zaharia2012resilient}}}{May. 2015}
%An xxx optimized for xxx\cite{verma2015large}
%\begin{itemize}
%  \item main contribution
%\end{itemize}

\section{\faCogs\ Skills}
\begin{itemize}[parsep=0.5ex]
  \item Programming Languages: Javascript (ES6, Vue/Vuex, React/Redux, Nodejs) > Golang (Beego) > PHP > Python > C/C++ > Verilog > Java
  \item Databases: Mysql > Mongodb
  \item Version control: Git
  \item Platform: Windows/Linux
  \item Development: Web (Full Stack)
  \item Other: Familiar with TCP/IP and network programming
\end{itemize}

\section{\faHeartO\ Honors and Awards}
\datedline{\textit{\nth{3} Prize}, Award on National University Student Mathematical Modeling Competition}{Sep. 2017}
\datedline{\textit{\nth{5} Prize}, Award on hack.init()}{July. 2017}
\datedline{Grade B excellent scholarships}{Sep. 2016}
\datedline{\textit{\nth{3} Prize}, Award on Intel hackathon}{Oct. 2016}
\datedline{\textit{\nth{3} Prize}, Award on National Mathematics Competition}{Oct. 2014}
\datedline{\textit{\nth{1} Prize}, Award on Shanghai TI mathematics competition}{June. 2013}

\section{\faInfo\ Miscellaneous}
\begin{itemize}[parsep=0.5ex]
  \item GitHub: https://github.com/shinytang6
  \item Languages: English - Fluent, Chinese - Native speaker
\end{itemize}

%% Reference
%\newpage
%\bibliographystyle{IEEETran}
%\bibliography{mycite}
\end{document}
